Multi-view 3D Aerosol Distribution Recovery

### 2013-07-30 article.tex
reviewing Yoav changes

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%% body %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Optical lightfield and integral
imaging~\cite{Stern2006,kim,Ng1948} samples the optical
radiance distribution in location and direction. It is mainly used in
small-scale setups. This paper deals with a far larger scale, to
estimate scatterer 3D spatial distribution in the sky.  The atmosphere
allows light to pass through in multiple locations and
directions. Light is affected by this medium. Therefore, in this paper
we lay out a principle to recover this 3D distribution using measured
and modeled light-fields (Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

@@

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details.

\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$. Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
  B}=255:236:224$.

\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
  50}{\km} extending from the ground up to altitude of
\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
different grid sizes from \num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}
and up to \num{50 x 50 x 100} grid, where each voxel has area of \SI{1
  x 1}{\km} and vertical thickness of \SI{100}{\metre}.

@@

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution ${\bm n}$.
% Most generally, this is the set $\left\{{\bm
%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
% parameters depend on the spectral channel $\lambda$.  Usually, a
% single aerosol type dominates a scene. Furthermore, we assume that
% the type of the aerosol above an area is
% known~\cite{Martonchik2009}. Hence, we focus on estimating the
% density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalized energy in second order spatial derivatives
(3D Laplacian). Hende, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.

@@

The goal, of coarse, is to deploy such a system on a very large
scale. However, this must first ensure that camera units are both cost
effective and field-robust, and that their positioning density is
proper. This will require a long-term engineering effort. Camera
specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research and development phase.  The new sensing modality and object
of interest offer a new domain for computational photography
problems. For example, how can compressed sensing principles be
employed here? How can priors be used to make data acquisition more
efficient? How can such a system be calibrated over time? Many such
questions and solutions would rise.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% Appendix %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\appendix
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \section{Gradient Derivation}
% \label{sec:gradient-derivation}
%
% Here we detail the derivation of the Jacobian ${\bm J}_{{\bm
% i}_c}({\bm n})$ from \cref{eq:gradient1}. First show some results
% relating to differentiation.  Let
% $\vect{a}(\vect{n}),\vect{u}(\vect{n})$ be vector functions: each
% outputs a vector of length $r$. Let $\mat{C}$ be a $r \times N_{\rm
% voxels}$ matrix, where $N_{\rm voxels}$ is the length of ${\bm n}$.
% Then,
% \begin{align}
%   \label{eq:partial1}
%   \PartDeriv{\transpose{\mat{C}} (\vect{a} \odot
%   \vect{u})}{\vect{n}}
%   = \left[ \PartDeriv{\vect{a}}{\vect{n}} \OpDiag{\vect{u}} +
%     \PartDeriv{\vect{u}}{\vect{n}} \OpDiag{\vect{a}} \right]
%   \mat{C}.
% \end{align}
% Here we denote by $\OpDiag{\vect{v}}$ conversion of a general vector
% $\vect{v}$ into a diagonal matrix, whose main diagonal elements
% correspond to the elements of $\vect{v}$. Now, let
%% \begin{align}
%   $\vect{a}(\vect{n}) = \exp(-{\mat{C}}\vect{n})$,
%%   \label{eq:example1}
%% \end{align}
%% In \cref{eq:example1},
% where the exponent is element-wise (not raising an operator to some
% power). Then
% \begin{align}
%   \label{eq:partial2}
%   \PartDeriv{\vect{a}}{\vect{n}} &= - \transpose{\mat{C}} \,
%   \OpDiag{\exp(-{\mat{C}}\vect{n})}.
% \end{align}
% Using \cref{eq:partial2},
% \begin{align}
%   \label{eq:partial4}
%   \PartDeriv{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
%   aerosol}{\bm D}_c {\bm n})]}
%   {\vect{n}} &= - {\sigma}^{\rm aerosol}\transpose{\OpDistance_c} \,
%   \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} + {\sigma}^{\rm
%   aerosol}{\bm D}_c {\bm n})]},
% \end{align}
% where $\vect{\tau}_c^{\rm air}$ is independent of ${\bm n}$. Using
% \cref{eq:partial1},
% \begin{align}
%   \label{eq:partial3}
%   \PartDeriv{\, [\varpi^{\rm aerosol}\sigma^{\rm aerosol} P^{\rm
%   aerosol}_g(\vect{\Phi}^{\rm scatter}_c) \odot{\bm n}]}{\vect{n}}
%   = \varpi^{\rm aerosol}\sigma^{\rm aerosol}\OpDiag{P^{\rm
%   aerosol}_g(\vect{\Phi}^{\rm scatter}_c)}.
% \end{align}
% Based on \cref{eq:partial4,eq:partial1,eq:partial3} we derive the
% Jacobian of \cref{eq:bigIA} in close-form,
% \begin{align}
%%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm
%%   TOA}(\abbrev{A}-\abbrev{B})\abbrev{C}
%   {\bm J}_{{\bm i}_c}({\bm n}) &= L^{\rm TOA}{\sigma}^{\rm
%   aerosol}({\bf A}-{\bf B}) \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
%   {\sigma}^{\rm aerosol} {\bm D}_c {\bm n})]}
%   \transpose{{\vect{\Pi}}_c} ,
%   \label{eq:gradient2}
% \end{align}
% where
%% \begin{align}
%%   \label{eq:gradient3}
%%   {\bf A} &= \varpi^{\rm aerosol}
%%   \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)} \nonumber\\
%%   {\bf B} &= \transpose{{\bm D}_c} %\nonumber\\
%%%   & \;\;\;
%%   \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
%%   aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
%%   scatter}_c) \odot{\bm n} ]}
%%    %   \nonumber \\
%%  %   \abbrev{C} &= \OpDiag{\exp[-(\vect{\tau}_c^{\rm air} +
%%  %   {\sigma}^{\rm
%%   %   aerosol} {\bm D}_c {\bm n})]} \transpose{{\vect{\Pi}}_c}
%% \end{align}
% \begin{equation}
%  \label{eq:gradient3}
%  {\bf A} = \varpi^{\rm aerosol}
%       \OpDiag{ P_g^{\rm aerosol}(\vect{\Phi}^{\rm scatter}_c)}
%  ,\;\;\;
%  {\bf B} = \transpose{{\bm D}_c}
%      \OpDiag{[\tilde{\vect{\alpha}}^{\rm air}_c + \varpi^{\rm
%      aerosol}\sigma^{\rm aerosol} P^{\rm aerosol}_g(\vect{\Phi}^{\rm
%      scatter}_c) \odot{\bm n}    ]}
%\end{equation}

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%% References %%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%% body %%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Optical lightfield and integral
imaging~\cite{Stern2006,kim,Ng1948} sample the optical
radiance distribution in location and direction. These are mainly used in
small-scale setups. This paper deals with a far larger scale, to
estimate scatterer 3D spatial distribution in the sky.  The atmosphere
allows light to pass through in multiple locations and
directions. Light is affected by this medium. Therefore, in this paper
we lay out a principle to recover this 3D distribution using measured
and modeled light-fields (Fig.~\ref{fig:groundgrid}).
\begin{figure*}[t!]
  \begin{center}
    \yoavcomment{\includegraphics[width=\linewidth]{images/groundtomog24.pdf}}
  \end{center}
  \caption{\small Lightfield imaging through a volumetric distribution
    in the atmosphere, using ground-based cameras.}
  \label{fig:groundgrid}
\end{figure*}
3D recovery of this medium has direct implications to various
scientific communities that either rely on remotely-sensed imagery,
study the atmosphere, or overcome the medium to see beyond. These
include meteorology, atmospheric sciences, volcanology, and
climatology.  Aerosol retrieval is important for understanding climate
evolution~\cite{Dayan2008,kalashnikova} and monitoring air
quality. Mapping aerosol density is significant to aviation safety,
which needs real time assessment of conditions and visibility around
flight paths.

@@

\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{0.95\columnwidth}\input{images/ref_images.pdf_tex}}
  \caption{\small [a] Photograph of a sky that includes {\em Haze
      Blobs} rendered using the single-scattering model.  A yellow dot
    marks the Sun location. Dashed white circles mark elevation
    angles.  [b] Photograph of the same sky and view point rendered
    using the MC simulation (\cref{sec:monte-carlo-simul}).  [c] Cross
    section along the X-Axis of the MC simulation, Single-Scattering
    simulation and a Single-Scattering image created from the
    reconstructed distribution (\cref{sec:optimization-results}).}
  \label{fig:simulation-results1}
\end{figure}
To test the models, we simulated several atmospheric scenarios. Here
are the details:
\\

\noindent{\bf Sun}: The sun is at zenith angle $\Phi^{\rm
  SR}=45^o$. Its $L^{\rm TOA}$ is obtained
from~\cite{BBradiance,sun_composition}, with respective red-green-blue
ratios of $L^{\rm TOA}_{\rm R}:L^{\rm TOA}_{\rm G}:L^{\rm TOA}_{\rm
  B}=255:236:224$.
\\

\noindent{\bf Dimensions}: The sky domain has area of \SI{50 x
  50}{\km} extending from the ground up to altitude of
\SI{10}{\km}. This volume is divided into a rectilinear grid. We used
different grid sizes from \num{10 x 10 x 20} grid, where each voxel
has area of \SI{5 x 5}{\km} and vertical thickness of \SI{500}{\metre}
and up to \num{50 x 50 x 100} grid, where each voxel has area of \SI{1
  x 1}{\km} and vertical thickness of \SI{100}{\metre}.
\\

@@

The second function, $w_2$, expresses a clustered nature of aerosol
``clouds''. We define blobs in the form of 3D ellipsoids. There may be
multiple ellipsoids suspended.  Then
\begin{equation}
  w_2(k) =
  \left\{
    \begin{array}{ll}
      1  & \mbox{ if $k\in$ any blob cluster} \\
      0  & \mbox{ otherwise}
      \label{eq:f2}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The true aerosol distribution is then
\begin{equation}
  \label{eq:ntrue}
  {\bm n}^{\rm true}={\bm w}_1\odot {\bm w}_2  .
  \hspace{-0.05cm}
\end{equation}
As an example, we created a {\em Haze Blobs} scene using two ellipsoid
blobs (\cref{fig:results}a): the first is centered at altitude
\SI{3.3}{\km}, and has horizontal width of \SI{32}{\km} and vertical
thickness of \SI{2.8}{\km}. The second ellipsoid is centered at
altitude \SI{6.6}{\km}, and has lateral width of \SI{24}{\km} and
vertical thickness of \SI{2.1}{\km}. Note that the horizontal widths
are much larger than the vertical ones. This is consistent with scales
of atmospheric aerosol distributions.
\\

@@

In this paper, we assume that the type of the aerosol above an area is
known~\cite{Martonchik2009}. Hence, we focus on estimating the density
distribution ${\bm n}$.
% Most generally, this is the set $\left\{{\bm
%   n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
%     g}_{\lambda}\right\}_{\lambda}\right\}$ where some of the
% parameters depend on the spectral channel $\lambda$.  Usually, a
% single aerosol type dominates a scene. Furthermore, we assume that
% the type of the aerosol above an area is
% known~\cite{Martonchik2009}. Hence, we focus on estimating the
% density distribution ${\bm n}$.
At hand, we have $N_{\rm views}$ measured photographs $\{ {\bm i}^{\rm
  measured}_c\}_{c=1}^{N_{\rm views}}$. The recovery task is phrased
as optimization of an objective function that fits the image-formation
model to the measured photographs:
\begin{equation}
  \label{eq:minobjectiveA}
  \hat{\bm n} =
  \argmin_{{\bm n}} F({\bm n})
\end{equation}
where
\begin{equation}
  \label{eq:objectiveA}
  F({\bm n})
  = \sum_{c=1}^{N_{\rm views}}
  \| \Mask \roundy{{\bm i}^{\rm measured}_c - {\bm i}_c({\bm n})}\|^2_2
  + \eta \Psi({\bm n})
\end{equation}
where $\Mask$ is a map that masks the areas around the sun, which are
overwhelmingly bright. %and the horizon.
% These regions are prone to dominant multiple scattering.
In Eq.~(\ref{eq:objectiveA}), $\Psi({\bm n})$ is a regularization term
that expresses some prior knowledge on the distribution, while $\eta$
is a regularization weight.  Since aerosol distributions are usually
fuzzy, it can be beneficial that regularization be a {\em smoothness
  term}, which penalizes energy in second order spatial derivatives
(3D Laplacian). Hence, we use
\begin{equation}
  \label{eq:regularizer}
  \Psi({\bm n}) = \| \nabla^2{\bm n}\|^2_2 = \| \Laplacian{\bm n}\|^2_2
\end{equation}
where $\Laplacian$ is a matrix representation of the 3D
\emph{Laplacian} operator.

@@

The goal, of coarse, is to deploy such a system on a very large
scale. However, it must be first ensured that camera units are both
cost effective and field-robust, and that their positioning density is
proper. This will require a long-term engineering effort. Camera
specifications should be set to optimally recover a wide range of
aerosol distributions. This requires a major theoretic and numerical
research and development phase.  The new sensing modality and object
of interest offer a new domain for computational photography
problems. For example, how can compressed sensing principles be
employed here? How can priors be used to make data acquisition more
efficient? How can such a system be calibrated over time? Many such
questions and solutions would rise.
